---
title: "Descriptive Statistics (Demographics)"
---

```{r}
#| label: setup
#| include: false

# Eksekusi unduh data (menghasilkan data/cleaned_data.rds & db_info.rds)
source("R/setup_data.R")

# Load helper functions
source("R/helpers.R")
library(ggplot2)
library(dplyr)

# Baca data
db_info <- readRDS("data/db_info.rds")
df <- readRDS("data/cleaned_data.rds")
```
::: {.callout-note}
## Note
This file contains the main analysis for measurement model testing (CFA) and scale reliability integrated in real-time with the primary database.
:::


## Database & Respondent Processing

Respondent data is automatically pulled from [Google Sheets](https://docs.google.com/spreadsheets/d/1u7L4GSSsuVDv9j7ccgWvccwr7A5Ks0szkiY-RTHVsA8/edit?usp=sharing) (Scoring). Subsequently, the data is checked and filtered according to predetermined criteria to obtain data that is ready to use.

**Last updated:** `r db_info$waktu_update`

Below is the data filtering process from incoming respondents to the final data.


<div style="display: flex; gap: 1rem; flex-wrap: wrap; margin-bottom: 2rem; justify-content: space-between;">
<div style="flex: 1; min-width: 200px; background: #f8f9fa; border-top: 5px solid #4e79a7; border-radius: 8px; padding: 1.5rem; text-align: center; box-shadow: 0 2px 4px rgba(0,0,0,0.1);">
<div style="margin: 0; color: #6c757d; font-size: 0.9rem; font-weight: bold; text-transform: uppercase; letter-spacing: 1px;">Total Respondents</div>
<div style="font-size: 3.5rem; font-weight: 800; color: #212529; margin: 0.5rem 0; line-height: 1;">`r db_info$total_masuk`</div>
<div style="font-size: 0.85rem; color: #6c757d;">Incoming Data</div>
</div>
<div style="flex: 1; min-width: 200px; background: #f8f9fa; border-top: 5px solid #e15759; border-radius: 8px; padding: 1.5rem; text-align: center; box-shadow: 0 2px 4px rgba(0,0,0,0.1);">
<div style="margin: 0; color: #6c757d; font-size: 0.9rem; font-weight: bold; text-transform: uppercase; letter-spacing: 1px;">Eliminated</div>
<div style="font-size: 3.5rem; font-weight: 800; color: #e15759; margin: 0.5rem 0; line-height: 1;">`r db_info$total_gugur`</div>
<div style="font-size: 0.85rem; color: #6c757d;">Excluded (Attention Check)</div>
</div>
<div style="flex: 1; min-width: 200px; background: #f8f9fa; border-top: 5px solid #59a14f; border-radius: 8px; padding: 1.5rem; text-align: center; box-shadow: 0 2px 4px rgba(0,0,0,0.1);">
<div style="margin: 0; color: #6c757d; font-size: 0.9rem; font-weight: bold; text-transform: uppercase; letter-spacing: 1px;">Final Data</div>
<div style="font-size: 3.5rem; font-weight: 800; color: #59a14f; margin: 0.5rem 0; line-height: 1;">`r db_info$total_valid`</div>
<div style="font-size: 0.85rem; color: #6c757d;">Passed Validity (Clean)</div>
</div>
</div>

***

After the filtering process is complete, a total of **`r nrow(df)` observations** are obtained which can be used for further analysis.

## Gender
```{r}
#| label: tbl-gender
#| tbl-cap: "Gender Distribution"
knitr::kable(print_demo_table(df$Gender, c("1" = "Male", "2" = "Female")))
```

```{r}
#| label: plot-gender
#| fig-cap: "Gender Visualization"
df %>% 
  filter(!is.na(Gender)) %>%
  mutate(Gender = factor(Gender, levels = c(1, 2), labels = c("Male", "Female"))) %>%
  ggplot(aes(x = Gender, fill = Gender)) +
  geom_bar(color = "black", alpha = 0.8) +
  scale_fill_manual(values = c("#4e79a7", "#e15759")) +
  labs(x = NULL, y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Age
```{r}
#| label: demografi-usia
usia_m   <- round(mean(df$Usia, na.rm = TRUE), 2)
usia_sd  <- round(sd(df$Usia, na.rm = TRUE), 2)
usia_min <- min(df$Usia, na.rm = TRUE)
usia_max <- max(df$Usia, na.rm = TRUE)
```
*M* = `r usia_m` years old, *SD* = `r usia_sd`, Min = `r usia_min`, Max = `r usia_max`.

```{r}
#| label: plot-usia
#| fig-cap: "Age Distribution Visualization"
df %>% 
  filter(!is.na(Usia)) %>%
  ggplot(aes(x = Usia)) +
  geom_histogram(binwidth = 1, fill = "#59a14f", color = "black", alpha = 0.8) +
  labs(x = "Age (Years)", y = "Count") +
  theme_minimal()
```

## Semester
```{r}
#| label: tbl-semester
#| tbl-cap: "Semester Distribution"
knitr::kable(print_demo_table(df$Semester, c("1" = "Semester 1", "2" = "Semester 2", "3" = "Semester 3", "4" = "Semester 4", "5" = "Semester 5", "6" = "Semester 6", "7" = "Semester 7", "8" = "Semester 8", "> Semester 8" = "> Semester 8")))
```

```{r}
#| label: plot-semester
#| fig-cap: "Semester Visualization"
df %>% 
  filter(!is.na(Semester)) %>%
  mutate(Semester = factor(Semester, 
                           levels = c("1", "2", "3", "4", "5", "6", "7", "8", "> Semester 8"), 
                           labels = c("Sem 1", "Sem 2", "Sem 3", "Sem 4", "Sem 5", "Sem 6", "Sem 7", "Sem 8", "> Sem 8"))) %>%
  ggplot(aes(x = Semester, fill = Semester)) +
  geom_bar(color = "black", alpha = 0.8) +
  labs(x = "Semester", y = "Count") +
  theme_minimal() +
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))
```

## Development Region (Residence)
```{r}
#| label: tbl-wilayah
#| tbl-cap: "Development Region Distribution"
knitr::kable(print_demo_table(df$Provinsi, c("1" = "Bodebekpunjur", "2" = "Purwasuka", "3" = "Sukabumi dsk", "4" = "Cekungan Bandung", "5" = "Priangan Timur", "6" = "Ciayumajakuning")))
```

```{r}
#| label: plot-wilayah
#| fig-cap: "Development Region Visualization"
df %>% 
  filter(!is.na(Provinsi)) %>%
  mutate(Provinsi = factor(Provinsi, 
                           levels = c("1", "2", "3", "4", "5", "6"), 
                           labels = c("Bodebekpunjur", "Purwasuka", "Sukabumi dsk", "Cekungan Bandung", "Priangan Timur", "Ciayumajakuning"))) %>%
  ggplot(aes(y = reorder(Provinsi, Provinsi, function(x) length(x)), fill = Provinsi)) +
  geom_bar(color = "black", alpha = 0.8) +
  labs(x = "Count", y = NULL) +
  theme_minimal() +
  theme(legend.position = "none")
```

## Living Area
```{r}
#| label: tbl-area
#| tbl-cap: "Living Area Distribution"
knitr::kable(print_demo_table(df$Area, c("1" = "Urban", "2" = "Suburban", "3" = "Rural")))
```

```{r}
#| label: plot-area
#| fig-cap: "Living Area Visualization"
df %>% 
  filter(!is.na(Area)) %>%
  mutate(Area = factor(Area, levels = c("1", "2", "3"), labels = c("Urban", "Suburban", "Rural"))) %>%
  ggplot(aes(x = Area, fill = Area)) +
  geom_bar(color = "black", alpha = 0.8) +
  scale_fill_manual(values = c("#76b7b2", "#f28e2b", "#edc948")) +
  labs(x = NULL, y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Housing Type
```{r}
#| label: tbl-hunian
#| tbl-cap: "Housing Type Distribution"
knitr::kable(print_demo_table(df$Hunian, c("1" = "Parent's House", "2" = "Boarding House", "3" = "Dormitory", "4" = "Other")))
```

```{r}
#| label: plot-hunian
#| fig-cap: "Visualisasi Tipe Hunian"
df %>% 
  filter(!is.na(Hunian)) %>%
  mutate(Hunian = factor(Hunian, levels = c("1", "2", "3", "4"), labels = c("Parent's House", "Boarding House", "Dormitory", "Other"))) %>%
  ggplot(aes(x = reorder(Hunian, Hunian, function(x) -length(x)), fill = Hunian)) +
  geom_bar(color = "black", alpha = 0.8) +
  labs(x = NULL, y = "Count") +
  theme_minimal() +
  theme(legend.position = "none")
```
